---
title: "gemaapp"
author: "Suschevskiy Vsevolod"
date: "1/26/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi Seva,

See attached the data.

<!-- You can find the full list of students who participated in the survey in the data GameApp_SurveyRAW_Oct2020. We need to remove students who did not give consent. -->

<!-- We can get the list of students who used the game app and who did not use the game app based on this list. -->

We should only use two data file:

For the survey data: GameApp_SurveyRAW_Oct2020
For the gameapp usage: GameAppActivity

<!-- We can filter out the students who responded with a  2 in Q1 (1 means consent and 2 means non-consent) -->

My notes:
- look at activity data.
<!-- - What we agreed on is to look at the gameapp activity..filter the number of students who used the app from those who did not..the reference to this is the users from the survey (check above). -->
<!-- - play a bit with the data..show how much time each user spent on the questions. -->
<!-- - see how many days they used the app..and for how long? calculate from the timestamps. -->
<!-- - see if u can find something interesting? -->

- game mode usage 
- game modes (battel|compete) vs (practice|test)
- cluster analysis -- extract stratefies and compare them with outcomes
- questions about final grade
- exam dates
- 


If there are serious questions, email Jacqueline and put me in cc.

Let's surprise those guys in the Netherlands with some good work!

Best,

```{r}
library(tidyverse)
library(vroom)
library(lubridate)
# devtools::install_github("data-edu/tidyLPA")
# install.packages("MplusAutomation")
library(tidyLPA)
library(cli)

library(gt)
library(gtsummary)
library(ggpubr)

library(lavaan)
library(corrplot)
library(polycor)
library(sjmisc)
library(semPlot)

library(mgcv)
```

```{r}
activity <- vroom::vroom('GameAppActivity.csv')
survey <- vroom::vroom('GameApp_SurveyRAW_Oct2020.csv')
# exam <- vroom::v('GameAppExam.xlsx')
GameAppExam <- readxl::read_excel("~/SLATE/game_app/GameAppExam.xlsx")

survey = survey %>% 
  filter(Q1 != 2)
```

```{r}
survey = survey %>% 
  mutate(id = Q2 %>% str_extract("[:digit:].+[:digit:]"))

activity = activity %>% 
  mutate(id = username %>% str_extract_all("[:digit:].+[:digit:]"))
```


#### counts

```{r}
survey %>% 
  filter(Q1 != 2) %>% 
  count(id)



activity %>% 
  count(id)
```


```{r}
activity = activity %>% 
  mutate(srv = case_when(
    id %in% survey$id ~ TRUE,
    TRUE ~ FALSE
  ))

activity %>% 
  count(id)
```

```{r}
activity = activity %>% 
  select(-time_to_answer) %>% 
  unique() %>% 
  mutate(timestamp = ymd_hms(timestamp)) %>% 
  arrange(timestamp, username) %>% 
  group_by(username) %>% 
  mutate(time_dif = timestamp - lag(timestamp),
         time_diff_sec = as.numeric(time_dif, units = 'secs'))
```

```{r}
activity$time_diff_sec  %>%  summary()

activity %>% 
  filter(time_diff_sec >= 0 & time_diff_sec < 120) %>% 
  ggplot(aes(x = time_diff_sec, fill = as.factor(correct)))+
  geom_histogram(binwidth = 1, alpha = 0.9)+
  theme_minimal()
```

```{r}
activity %>% 
  # filter(time_diff_sec >= 0 & time_diff_sec < 120) %>% 
  group_by(username, correct) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x = as.factor(correct), y = n))+
  geom_violin()+
  theme_minimal()
```

```{r}
library(gganimate)

top_users = activity %>% 
  ungroup() %>% 
  count(username) %>% 
  arrange(n)
  slice_max(n, n = 20) %>% .$username


activity %>% 
  filter(username %in% top_users) %>% 
  mutate(score = case_when(
    correct == 1 ~ 1,
    TRUE ~ -1
  )) %>% 
  group_by(id) %>%
  arrange(timestamp) %>% 
  mutate(n = row_number(),
cum_score = cumsum(score),
id = as.factor(id)
         ) %>% 
  filter(n < 120) %>% 
  ggplot(aes(x = n, y = cum_score, color = id))+
  geom_line() +
  scale_color_viridis_d() +
  labs(x = "Exercises", y = "Scores") +
  theme_minimal()+
  theme(legend.position = "top")-> p
  


p +
  geom_point() +
  transition_reveal(n)
```

```{r}
names(survey)
```


```{r}
survey$`Q7_5...17`
```

```{r}
GameAppExam$`MC-SCORE (max 60)` %>% 
  plot()


GameAppExam[,2:3] %>% 
  plot()
```

## Measurments

### Advanced planning 

```{r}
gl <- function(x) {
  y <- c(unclass(diff(x)))  # c and unclass -- preparing it for rle
  r <- rle(y)
  z <- with(r, max(lengths[values==1]))
  if (z < 0) {
    z = 0
  }
  return(z)
}

?rle

activity_adv <- activity %>% 
  ungroup() %>% 
  mutate(day = floor_date(timestamp, 'days') ) %>% 
  select(id, day) %>% 
  unique() %>% 
  group_by(id) %>% 
  summarise(
    max.consecutive = gl(day) + 1,
    max.n =  n(),
    min.far = difftime(ymd('2018-03-09'), min(day)) %>% as.numeric(),
    max.far = difftime(ymd('2018-03-09'), max(day)) %>% as.numeric()
  )


activity_adv %>% 
  ggplot(aes(x = max.consecutive))+
  geom_boxplot()
```

### timediff

```{r}
activity_time <- activity %>% 
  filter(time_diff_sec >= 0 & time_diff_sec < 120) %>% 
  group_by(id) %>% 
  summarise(m.time = median(time_diff_sec), min.time = min(time_diff_sec), max.time = max(time_diff_sec))

activity_time %>% 
  ggplot()+
  geom_boxplot(aes(x = m.time))
```

### game profiles

```{r}
activity_modes <- activity %>% 
  ungroup() %>% 
  mutate(game_mode_id =
           recode(
             game_mode_id,
             '1' = 'mode_practice',
             '2' = "mode_test",
             '3' = "mode_compete",
             '4' = "mode_battle"
           )) %>% 
  group_by(id, game_mode_id) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n / sum(n)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = game_mode_id, values_from = freq) %>% 
  mutate_all(~replace_na(., 0))

activity_modes_2 <- activity %>% 
  ungroup() %>% 
  mutate(game_mode_id =
           recode(
             game_mode_id,
             '1' = 'mode_practice',
             '2' = "mode_test",
             '3' = "mode_compete",
             '4' = "mode_battle"
           )) %>% 
  group_by(id, game_mode_id) %>% 
  summarise(n = n()) %>% 
  pivot_wider(names_from = game_mode_id, values_from = n) %>% 
  mutate_all(~replace_na(., 0))
  
activity_modes %>%
  pivot_longer(starts_with("mode"), names_to = "mode", values_to = "freq") %>% 
  ggplot() +
  geom_boxplot(aes(y = freq, x = mode))
```

### scores

```{r}
activity_scores = activity %>% 
  ungroup() %>% 
    mutate(correct =
           recode(
             correct,
             '1' = 'correct',
             '0' = "wrong"
           )) %>% 
  group_by(id, correct) %>% 
  summarise(n = n()) %>% 
  mutate(freq_correct = n / sum(n)) %>% 
  filter(correct == "correct") %>% 
  select(id, freq_correct)
```
### attempts

```{r}
activity_count = activity %>% 
  ungroup() %>% 
  group_by(id) %>% 
  count() %>% 
  rename('attempts' = 'n')
```


## lATENT profile

```{r}
GameAppExam%>% 
  rename(id = username, 
         mc = `MC-SCORE (max 60)`,
         open = `Open-ended questions (max 40)`) %>%
  unique() %>% 
  mutate_all(~as.numeric(.))-> GameAppExam

activity_adv %>% 
  left_join(activity_modes) %>% 
  left_join(activity_scores) %>% 
  left_join(activity_time) %>% 
  left_join(activity_count) %>% 
  unnest(id) %>% 
  left_join(GameAppExam %>% mutate(id = as.character(id))) %>% 
  left_join(activity_modes_freq %>% select(id, freq)) %>% 
  janitor::clean_names()-> df_comb
```

```{r}
df_comb$max_far %>% sd()
```

```{r}
# poms
#6
set.seed(26)

compare = df_comb %>%
  column_to_rownames('id') %>% 
  select(-starts_with("mode")) %>%
  select(-freq) %>%
  select(-mc, -open) %>%
  single_imputation() %>%
  tidyLPA::poms() %>% 
  estimate_profiles(
    1:7,
    variances = c("equal", "varying", 'equal', 'varying'),
    covariances = c("zero", "zero", 'equal',  'varying')
  ) %>%
  compare_solutions(statistics = c("AIC", "BIC", "AWE", "CLC","KIC"))

compare$fits %>% 
  select(Model ,Classes, AIC, BIC ,AWE ,CLC, KIC) %>%  write_csv(file = "LPA_fit.csv") #%>% 
  # na.omit() %>% 

# 'varying', 'equal'
# 'equal', 'varying',
# ?compare_solutions
```

```{r}
vroom::vroom("tidyLPA.txt")
```



```{r}
df_comb$max_n %>% summary()

 df_comb %>%
  column_to_rownames('id') %>% 
  select(-starts_with("mode")) %>%
  select(-freq) %>% 
  select(-mc, -open) %>%
  single_imputation() %>%
  # na.omit() %>%
  # scale() %>%
  rename(
    days_in_row = max_consecutive,
    use_days = max_n,
    start_early = min_far,
    finish_late = max_far,
    correct = freq_correct,
    mean_time = m_time,
    min_time = min_time,
    max_time = max_time
    # non_game_mode = freq
  ) %>% 
  # scale() %>% 
  poms() %>%
  estimate_profiles(3,
                    variances = "varying",
                    covariances = "zero") -> profiles

?poms
profiles %>% 
  plot_profiles(add_line =F, rawdata = T)

?plot_profiles
```

```{r}
profile_fit = get_fit(profiles)
gt::gt(profile_fit)
```

### DrAW LPA

```{r}
names(df_comb_lp)

df_comb_lp %>% group_by(Class) %>% 
  summarise(median(freq))

df_comb_lp %>%
  select(-starts_with("mode"), -mc, -open) %>%
    mutate(Class = fct_recode(Class, "Disengaged learners" = "1", "Active learners" = "2", "Utilitarian learners"="3")) %>% 
  select(-id) %>% 
    rename(
    'Days in a row' = max_consecutive,
    "Unique days" = max_n,
    "Early start" = min_far,
    "Late finish" = max_far,
    "Correct answers" = freq_correct,
    "Mean time" = m_time,
    "Minimum time" = min_time,
    "Maximum time" = max_time,
    "Frequency of mode" = freq,
    "Attempts"=attempts,
    "Exam grade" = sum
  ) %>% 
  select(-"Exam grade") %>% 
  single_imputation() %>% 
  poms()-> df_comb_lp_plot

df_comb_lp_plot %>% 
  pivot_longer(cols = c('Days in a row', "Unique days", "Early start", "Late finish", "Correct answers" ,"Mean time", "Minimum time", "Maximum time", "Frequency of mode", "Attempts"), names_to = "measures", values_to = "poms") ->df_comb_lp_plot

df_comb_lp_plot %>% 
  ggplot(aes(y = poms, x = measures, color = Class))+
  geom_jitter(position = position_jitter(seed = 2019, width = 0.3, height = 0.05), alpha = 0.3)+
  geom_point(
    data = data.frame(
      measures = c("Correct answers", "Days in a row"),
      poms = c(1 ,1),
      Class = c("Disengaged learners" ,"Active learners")
    ) ,
    alpha = 0.3
  )+
  # geom_boxplot(alpha = 0.5, outlier.shape = NA, coef = 0, fill = 1)+
  geom_boxplot(alpha = 0.5, outlier.shape = NA, coef = 0)+
  theme_bw()+
  ggtitle("Latent Profiles of Engagement" )+
  # theme(legend.position = "none") +
  # theme(text=element_text(size=12,  family="Helvetica"))+
  scale_color_brewer(palette = "Set2")+
  xlab("")+
  # coord_flip()+
  scale_x_discrete(guide = guide_axis(n.dodge=2))+
  theme(legend.position = c(0.9, 0.8),
      axis.title = element_text(size = 16),
      axis.text.x = element_text(family = "Roboto Mono", size = 12),
      axis.text.y = element_text(family = "Roboto Mono", size = 12),
      legend.text = element_text(family = "Roboto Mono", size = 10, color = "grey42"),
      legend.title = element_text(family = "Roboto Mono", size = 12, color = "grey52"),
      panel.grid = element_blank(),
      # legend.key = element_rect(color = NA, fill = NA),
      legend.key = element_rect(colour = "transparent", fill = alpha("red", 0))
)+
  # theme(legend.position = "none")+
  ylim(c(0, 1))+
    annotate(
    "text", x = 1.5, y = 0.85, family = "Poppins", size = 3, color = "gray20",
    label = "4090 attemps"
  )+
  annotate(
    "text", x = 5, y = 0.05, family = "Poppins", size = 3, color = "gray20",
    label = "2 days before \n the exam"
  )+
  annotate(
    "text", x = 6, y = 0.7, family = "Poppins", size = 3, color = "gray20",
    label = "13% of attemps \n in gamified modes"
  )+
  geom_curve(
    data = data.frame(
      x1 = c(1.5, 5, 6),
      y1 = c(0.87, 0.09 ,0.73),
      x2 = c(0.9, 4.4 ,5.2),
      y2 = c(0.97, 0.171, 0.867)
    ),
    aes(
      x = x1,
      y = y1,
      xend = x2,
      yend = y2
    ),
    arrow = arrow(length = unit(0.07, "inch")),
    size = 0.4,
    color = "gray20",
    curvature = 0.4
  )
?annotate


ggsave(filename = "LPA_GGPLOT3.png", width = 10, height = 5)

?geom_jitter
```



```{r}
df_comb %>%
  # select(-starts_with("mode")) %>%
  # select(-mc, -open) %>%
  single_imputation() %>%
  # na.omit() %>%
  mutate(Class = as.factor(get_data(profiles)$Class)) %>%
  # select(Class ,id) %>%
  # left_join(df_comb) %>%
  # na.omit() %>%
  ungroup()->df_comb_lp

df_comb_lp %>% 
  count(Class)

# get_data(profiles) -> df_comb_lp
```

```{r}
df_comb_lp %>%
  select(-starts_with("mode"), -mc, -open) %>%
    mutate(Class = fct_recode(Class, "Disengaged learners" = "1", "Active learners" = "2", "Utilitarian learners"="3")) %>% 
  group_by(Class) %>% 
  summarise_all(~mean(.) %>% round(3)) %>%  #median
  select(-id) %>% 
    rename(
    'Days in a row' = max_consecutive,
    "Unique days" = max_n,
    "Early start" = min_far,
    "Late finish" = max_far,
    "Correct answers" = freq_correct,
    "Mean time" = m_time,
    "Minimum time" = min_time,
    "Maximum time" = max_time,
    "Frequency of mode" = freq,
    "Attempts"=attempts,
    "Exam grade" = sum
  ) %>% 
  gt::gt() %>% 
    tab_header(
    title = "Median measures by class"
  ) %>% 
  tab_footnote(
    footnote = "Were not used in estimation of profiles.",
    locations = cells_column_labels(
      columns = c("Frequency of mode", "Exam grade")
    )
  ) %>% 
  gtsave(filename = "class_time.html")

?gtsave
?tab_footnote
?gt
```

1. Disengagement -- started early, finished early , made more mistakes and have not used for a while
2. Active users 
3. Exam preparation 


```{r}
df_comb_lp %>% 
ggplot(aes(x = max_n, color = Class))+
  geom_density()
```


```{r}
# ?kruskal.test
kruskal.test(mc ~ Class ,data = df_comb_lp)
kruskal.test(open ~ Class ,data = df_comb_lp)


# aov(mc ~ Class ,data = df_comb_lp) %>% summary()
# aov(open ~ Class ,data = df_comb_lp) %>% summary()

df_comb_lp$sum = df_comb_lp$mc+ df_comb_lp$open
aov(sum ~ Class ,data = df_comb_lp) %>% summary()
kruskal.test(sum ~ Class ,data = df_comb_lp)


# ?t.test
t.test(mc ~ Class ,data = df_comb_lp)
t.test(open ~ Class ,data = df_comb_lp)
```

```{r}
df_comb_lp %>% 
ggplot(aes(x = Class, y = mc))+
  geom_violin(aes(fill = Class), trim = FALSE) + 
  geom_boxplot(width = 0.2)+
    scale_fill_brewer(palette = "RdBu")+
  theme(legend.position = "none")+
  theme_bw()+
  ggtitle("Test scores")

df_comb_lp %>% 
ggplot(aes(x = Class, y = open))+
  geom_violin(aes(fill = Class), trim = FALSE) + 
  geom_boxplot(width = 0.2)+
    scale_fill_brewer(palette = "RdBu")+
  theme(legend.position = "none")+
  theme_bw()+
  ggtitle("Open question scores")
```

```{r}
df_comb_lp %>%
  mutate(grade = open + mc) %>%
  ggplot(aes(x = Class , y = grade)) +
  geom_violin(aes(color = Class), trim = F) +
  geom_jitter(aes(color = Class), alpha = 0.5) +
  stat_summary(
    fun.data = "mean_sdl",
    fun.args = list(mult = 1),
    geom = "pointrange",
    color = "black"
  ) +
  # scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  # scale_fill_brewer(palette = "RdBu") +
  scale_color_brewer(palette = "RdBu") +
  theme(legend.position = "none") +
  theme_bw() +
  ggtitle("grade")
```

```{r}
??tbl_summary
df_comb_lp %>%
  select(Class, starts_with("freq") ,mc, open) %>% 
  m
  tbl_summary(by = Class) %>% add_n() %>% add_p()
```



## Game modes

```{r}
df_comb %>% 
  ggplot(aes(x = mode_battle ,y = open))+
  geom_point()

activity_modes_2 %>%
  mutate(game_no = mode_practice + mode_test,
         game = mode_compete + mode_battle) %>%
  select(id, game_no , game) %>%
  unnest(id) %>%
  left_join(GameAppExam %>% mutate(id = as.character(id))) %>%
  janitor::clean_names() %>% 
  mutate(freq = game_no/(game + game_no) ) -> activity_modes_freq

activity_modes_freq %>% 
  ggplot(aes(x = game_no ,y = mc))+
  geom_point()+
  scale_x_log10()
```

```{r}
library(tidymodels)


set.seed(4595)
data_split <- initial_split(activity_modes_freq %>% na.omit(), strata = "mc", prop = 0.75)

act_train <- training(data_split)
act_test  <- testing(data_split)


```

```{r}
norm_recipe <- 
  recipe(
    mc ~ game + game_no, 
    data = act_train
  ) %>%
  # step_center(all_predictors()) %>%
  # step_scale(all_predictors()) %>%
  # step_log(all_predictors(), base = 10) %>%
  # estimate the means and standard deviations
  prep(training = act_train, retain = TRUE)

# Now let's fit the model using the processed version of the data

glmn_fit <- 
  linear_reg(penalty = 0.001, mixture = 0.5) %>% 
  set_engine("glmnet") %>%
  fit(mc ~ ., data = bake(norm_recipe, new_data = NULL))
glmn_fit
summary(glmn_fit)
```

```{r}

# First, get the processed version of the test set predictors:
test_normalized <- bake(norm_recipe, new_data = act_test, all_predictors())

test_results <- 
  act_test %>%
  select(mc) %>%
  bind_cols(predict(glmn_fit, new_data = test_normalized) %>%
              rename(glmnet = .pred)) %>% 
  ungroup() %>% 
  select(-id)
test_results
#> # A tibble: 731 x 3
#>    Sale_Price `random forest` glmnet
#>         <dbl>           <dbl>  <dbl>
#>  1       5.33            5.22   5.27
#>  2       5.02            5.21   5.17
#>  3       5.27            5.25   5.23
#>  4       5.60            5.51   5.25
#>  5       5.28            5.24   5.25
#>  6       5.17            5.19   5.19
#>  7       5.02            4.97   5.19
#>  8       5.46            5.50   5.49
#>  9       5.44            5.46   5.48
#> 10       5.33            5.50   5.47
#> # … with 721 more rows

test_results %>% metrics(truth = mc, estimate = glmnet) 


test_results %>% 
  gather(model, prediction, -mc) %>% 
  ggplot(aes(x = prediction, y = mc)) + 
  geom_abline(col = "green", lty = 2) + 
  geom_point(alpha = .4)
```

```{r}
df_comb_lp

m1 = lm(    mc ~ .-id-open, data = df_comb_lp)
summary(m1)
plot(m1)
```

## HDBSCAN

```{r}
df_comb %>%
  column_to_rownames('id') %>% 
  select(-starts_with("mode")) %>%
  select(-mc, -open) %>%
  single_imputation() %>%
  # na.omit() %>%
  # scale() %>%
  rename(
    consistency = max_consecutive,
    use_days = max_n,
    advanced_planning = max_far,
    correct = freq_correct,
    mean_time = m_time,
    min_time = min_time,
    max_time = max_time,
    non_game_mode = freq
  ) %>% 
  poms() -> df_comb_clean

?poms
```


```{r}
dbscan::kNNdistplot(df_comb_clean, k =  6)
abline(h = 0.44, lty = 2)
```


```{r}
library("dbscan")

# df_comb_clean

# ?hdbscan

cl <- hdbscan(df_comb_clean, minPts = 5)
cl
?dbscan
res.db <- dbscan::dbscan(df_comb_clean, 0.278, 4)
res.db
```

```{r}
plot(cl$hc, main="HDBSCAN* Hierarchy")
```


```{r}
check <- rep(F, nrow(df_comb_clean)-1)
core_dist <- kNNdist(df_comb_clean, k=5-1)

## cutree doesn't distinguish noise as 0, so we make a new method to do it manually 
cut_tree <- function(hcl, eps, core_dist){
  cuts <- unname(cutree(hcl, h=eps))
  cuts[which(core_dist > eps)] <- 0 # Use core distance to distinguish noise
  cuts
}

eps_values <- sort(cl$hc$height, decreasing = T)+.Machine$double.eps ## Machine eps for consistency between cuts 
for (i in 1:length(eps_values)) { 
  cut_cl <- cut_tree(cl$hc, eps_values[i], core_dist)
  dbscan_cl <- dbscan(df_comb_clean, eps = eps_values[i], minPts = 5, borderPoints = F) # DBSCAN* doesn't include border points

  ## Use run length encoding as an ID-independent way to check ordering
  check[i] <- (all.equal(rle(cut_cl)$lengths, rle(dbscan_cl$cluster)$lengths) == "TRUE")
}
print(all(check == T))
```

```{r}
plot(cl ,show_flat = T)
```

```{r}
plot(df_comb_clean, col=cl$cluster+1, pch=21)
  colors <- mapply(function(col, i) adjustcolor(col, alpha.f = cl$membership_prob[i]), 
                   palette()[cl$cluster+1], seq_along(cl$cluster))

points(df_comb_clean, col=colors, pch=20)
```

```{r}
print(cl$cluster_scores)
  head(cl$membership_prob)
```

```{r}
install.packages("uwot")
library(uwot)

df_umap <- umap(df_comb_clean)

plot(df_umap)
```

```{r}
df_umap %>% 
  as_tibble() %>% 
ggplot(aes(x = V1 ,y = V2))+
  geom_point(color = as.factor(cl$cluster +1))+
  ggtitle("hdbscan")
```

```{r}
df_umap %>% 
  as_tibble() %>% 
ggplot(aes(x = V1 ,y = V2))+
  geom_point(color = as.factor(res.db$cluster +1))+
  ggtitle("Ddbscan")

```


```{r}
df_umap %>% 
  as_tibble() %>% 
ggplot(aes(x = V1 ,y = V2))+
  geom_point(color = as.factor(df_comb_lp$Class))+
  ggtitle("Latent profiles")
```

### Survey 2 

```{r}
library(foreign)

survey2 <- read.spss("~/SLATE/game_app/GameAppSurvey2_TranslatedClean7Dec.sav", to.data.frame=TRUE)

library(haven)

survey2 = read_sav("~/SLATE/game_app/GameAppSurvey2_TranslatedClean7Dec.sav")
survey2 %>% 
  rename(id = ERNA)
```




### Chiq

```{r}
df_comb_lp %>% 
  pivot_longer(starts_with("mode"), names_to = "mode", values_to = "mode_share") %>% 
  group_by(id) %>% 
  filter(mode_share == max(mode_share)) %>% 
  ungroup() -> df_chi

library(infer)

df_chi %>% 
  specify(mode ~ Class) %>%
  # hypothesize(null = "independence") %>%
  # generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") -> observed_indep_statistic
observed_indep_statistic
```

```{r}
null_distribution_simulated <- df_chi %>% 
  specify(mode ~ Class) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq")

null_distribution_theoretical <- df_chi %>%
  specify(mode ~ Class) %>%
  hypothesize(null = "independence") %>%
  # note that we skip the generation step here!
  calculate(stat = "Chisq")
```


```{r}
null_distribution_simulated %>%
  visualize() + 
  shade_p_value(observed_indep_statistic,
                direction = "greater")
```

```{r}
# visualize both null distributions and the test statistic!
null_distribution_simulated %>%
  visualize(method = "both") + 
  shade_p_value(observed_indep_statistic,
                direction = "greater")
```

```{r}
p_value_independence <- null_distribution_simulated %>%
  get_p_value(obs_stat = observed_indep_statistic,
              direction = "greater")

p_value_independence
```

```{r}
chisq_test(df_chi, mode ~ Class)
```

```{r}
library("vcd")
df_chi %>%
  count(mode, Class) %>%
  pivot_wider(
    names_from = Class,
    names_prefix = "class_",
    values_from = n,
    values_fill = 0
  ) %>%
  column_to_rownames('mode') %>% 
  as.matrix() %>% 
  as.table() -> table_chi

# plot just a subset of the table
assoc(table_chi, shade = TRUE, las=3)
```

```{r}
library(tidystats)
fisher.test(mode ~ Class, data = df_chi)
?fisher.test

tab <- janitor::tabyl(df_chi, Class, mode)
tab

stats::fisher.test(table_chi ,workspace = 2e8, hybrid = T, simulate.p.value = T)
```
<!-- ## expected grade -->

<!-- ```{r} -->
<!-- GameApp_SurveyRAW_Oct2020 <- read_csv("~/SLATE/game_app/GameApp_SurveyRAW_Oct2020.csv") -->

<!-- GameApp_SurveyRAW_Oct2020 -->
<!-- ``` -->

## survey profiles


```{r}
survey1clean %>% 
  select(ends_with("Mean"), username) -> survey_lpa
survey_lpa
```

```{r}
survey_lpa %>%
  as_tibble() %>% 
  column_to_rownames('username') %>%
  single_imputation() %>%
  tidyLPA::poms() %>% 
  estimate_profiles(
    1:8,
    variances = c("equal", "varying", 'equal', 'varying'),
    covariances = c("zero", "zero", 'equal',  'varying')
  ) %>%
  compare_solutions(statistics = c("AIC", "BIC", "AWE", "CLC","KIC"))
```


```{r}
survey_lpa %>%
  as_tibble() %>% 
  column_to_rownames('username') %>%
  single_imputation() %>%
  # scale() %>% 
  tidyLPA::poms() %>%
  estimate_profiles(
    3,
    variances = c('varying'),
    covariances = c('varying')
  ) -> profiles_2

profiles_2

profiles_2 %>% 
  plot_profiles(add_line =F, rawdata = T)
```

## Pvalue plot

```{r}
?compare_means
library(ggpubr)
test = compare_means(sum ~ Class, p.adjust.method = "holm",  data = df_comb_lp %>% 
                       filter(!id %in% c("485167", "482613" ,"73834")))
test
```


```{r}

my_comparisons <- list( c("1", "2"), c("1", "3"), c("2", "3") )

ggboxplot(df_comb_lp, x = "Class", y = "sum",
          palette = "jco")+ 
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 120)#+     # Add global p-value+
  # stat_pvalue_manual(test, label = "p.adj.signif", tip.length = 0.01)
```

```{r}
my_comparisons <- list( c("Disengaged learners", "Active learners"), c("Disengaged learners", "Utilitarian learners"), c("Active learners", "Utilitarian learners") )

g_grade = df_comb_lp %>% 
  mutate(Class = fct_recode(Class, "Disengaged learners" = "1", "Active learners" = "2", "Utilitarian learners"="3")) %>% 
  filter(!id %in% c("485167", "482613" ,"73834")) %>% 
  ggplot(aes(x = Class, y = sum)) +
  geom_violin( trim = T) +
  geom_jitter(alpha = 0.3) +
  stat_compare_means(comparisons = my_comparisons) + # Add pairwise comparisons p-value
  stat_compare_means(label.y = 120)+#+     # Add global p-value+
  # stat_pvalue_manual(test, label = "p.signif", tip.length = 0.01)
    stat_summary(
    fun.data = "mean_sdl",
    fun.args = list(mult = 1),
    geom = "pointrange",
    color = "black"
  ) +
    theme(legend.position = "none") +
  theme_bw() +
  theme(text=element_text(size=16,  family="Helvetica"))+
  scale_color_brewer(palette = "RdBu") +
  ggtitle("Exam grade by class")+
  ylab("Exam scores")

g_grade

ggsave(filename = "grade_class_2.png", width = 8, height = 5)
```

```{r}
my_comparisons <- list( c("Disengaged learners", "Active learners"), c("Active learners", "Non-users") )

g_grade_2 = poor_model_scores %>% 
  mutate(class = fct_recode(class, "Disengaged learners" = "1", "Active learners" = "2", "Utilitarian learners"="3" ,"Non-users" = "4")) %>% 
  ggplot(aes(x = class, y = TM)) +
  geom_violin( trim = T) +
  geom_jitter(alpha = 0.3) +
  stat_compare_means(comparisons = my_comparisons) + # Add pairwise comparisons p-value
  stat_compare_means(label.y = -1)+#+     # Add global p-value+
  # stat_pvalue_manual(test, label = "p.signif", tip.length = 0.01)
    stat_summary(
    fun.data = "mean_sdl",
    fun.args = list(mult = 1),
    geom = "pointrange",
    color = "black"
  ) +
    theme(legend.position = "none") +
  theme_bw() +
  theme(text=element_text(size=16,  family="Helvetica"))+
  scale_color_brewer(palette = "RdBu") +
  ggtitle("Time Management by class")+
  ylab("Time Management")

g_grade_2

ggsave(filename = "TM_class_2.png", width = 8, height = 5)
```


## dunn test

```{r}
library(rstatix)
# ??dunn_test
df_comb_lp %>% dunn_test(sum ~ Class)

poor_model_scores %>% dunn_test(final_grade ~ class)
poor_model_scores %>% dunn_test(TM ~ class)
```

## Game mode 

### game mode and class

```{r}
kruskal.test(freq ~ Class ,data = df_comb_lp)
```

```{r}
df_comb_lp %>%
  ggplot(aes(x = Class , y = freq)) +
  geom_boxplot(aes(color = Class), trim = F) +
  geom_jitter(aes(color = Class), alpha = 1) +
  stat_summary(
    fun.data = "mean_sdl",
    fun.args = list(mult = 1),
    geom = "pointrange",
    color = "black"
  ) +
  # scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  # scale_fill_brewer(palette = "RdBu") +
  # scale_color_brewer(palette = "RdBu") +
  theme(legend.position = "none") +
  theme_bw() +
  ggtitle("freq in non game mode")
```

```{r}
df_comb_lp %>% dunn_test(freq ~ Class)
```

```{r}
9.287330e-02
```


### game mode and grades

```{r}
df_comb_lp %>% 
  ggplot(aes(x = freq, y = sum))+
  geom_point()
```

```{r}
cor.test(df_comb_lp$freq, df_comb_lp$sum, method=c("spearman"))
```


## Corelation with survey

### ANOVA

```{r}
df_comb_lp %>%
  left_join(survey_lpa %>% mutate(username = username %>% as.numeric()),
            by = c("id" = "username")) %>% 
  filter(GSL_Mean != "NaN") %>% 
  na.omit() -> survey_app


```


```{r}
survey_app %>%
  mutate(final_grade =  mc + open) %>% 
  # poms() %>% 
  mutate(app_act = max_n +  attempts +  max_consecutive) %>% 
  select(Class, final_grade, app_act , ends_with("Mean")) %>% 
  tbl_summary(by = Class) %>% add_n() %>% add_p()
```

```{r}
survey_app %>%
  mutate(final_grade =  mc + open) %>% 
  mutate(app_act = scale(max_n) + scale(attempts) + scale(max_consecutive)) %>% 
  select(Class, final_grade, app_act , ends_with("Mean")) %>% 
  tbl_summary(by = Class) %>% add_n() %>% add_p()
```


```{r}
survey_app %>%
  mutate(final_grade =  mc + open) %>%
  mutate(app_act = scale(max_n) + scale(attempts) + scale(max_consecutive)) %>%
  select(-sum,
         -max_n,
         -attempts ,
         -max_consecutive,
         -mc,
         -open,
         -starts_with("mode")) %>%
  select(-id, -Class) %>% 
  scale() %>% 
  as_tibble() ->
  sa_scaled
```


```{r}
sa_scaled
cor.test(sa_scaled$app_act, sa_scaled$CMG_Mean, method=c("spearman"))
cor.test(sa_scaled$app_act, sa_scaled$CPG_Mean, method=c("spearman"))
cor.test(sa_scaled$app_act, sa_scaled$APG_Mean, method=c("spearman"))
cor.test(sa_scaled$app_act, sa_scaled$AMG_Mean, method=c("spearman"), exact=FALSE)
```

```{r}
sa_scaled %>% 
ggplot(aes(x = app_act, y = AMG_Mean))+
  geom_jitter()
```

```{r}
library(corrplot)
M<-cor(sa_scaled %>%   
  #        rename(
  #   # consistency = max_consecutive,
  #   # use_days = max_n,
  #   advanced_planning = max_far,
  #   correct = freq_correct,
  #   mean_time = m_time,
  #   min_time = min_time,
  #   max_time = max_time,
  #   freq = freq
  # ) 
        rename(
    # 'Days in a row' = max_consecutive,
    # "Unique days" = max_n,
    "Early start" = min_far,
    "Late finish" = max_far,
    "Correct answers" = freq_correct,
    "Mean time" = m_time,
    "Minimum time" = min_time,
    "Maximum time" = max_time,
    "Frequency of mode" = freq,
    # "Attempts"=attempts,
    # "Exam grade" = sum
  )
  )

cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(sa_scaled)
head(p.mat[, 1:5])

res1 <- cor.mtest(sa_scaled, conf.level = .95, method = "spearman")
?cor.mtest
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
pdf(file = "corplot.pdf")
corrplot(M, 
         # title = "Spearman correlation. Survey and application",
         method="color", col=col(200),  
         type="lower", order="hclust", 
         # addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=30, tl.offset = 0, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=F 
         )
dev.off()
# ?corrplot

?corrplot
```

## if i read your correlations table correctly, final grade is weakly correlated with only freq_correct? 

```{r}
corrplot(M, p.mat = res1, sig.level = .05)
```



## PArtial correlation network

```{r}


library('bootnet')
# results <- estimateNetwork(data,
#                            default = "EBICglasso",
#                            corMethod = "cor_auto",
#                            tuning = 0.5)

network <- estimateNetwork(sa_scaled ,
                           default = "EBICglasso",
                           corArgs = list(method = "spearman"),
                           tuning = 0.5,
                           refit = TRUE)
```

```{r}
network %>% summary()
```

```{r}
dev.new(width=10, height=12)
plot(network)
```


```{r}
simRes <- netSimulator(
  network$graph,
  dataGenerator = ggmGenerator(ordinal =
                                 TRUE, nLevels = 5),
  default = 'EBICglasso',
  nCases = c(100, 250, 500, 1000, 2500),
  tuning = 0.5,
  nReps = 100,
  nCores = 8
)
```

```{r}
simRes
```
```{r}
plot(simRes)
plot(simRes, yvar = c('strength', 'closeness',
                      'betweenness'))
```


## part time and full time students 

if we can make a distinction between part time and full time students (or maybe not, because the numbers are too low?) The part time and full time question refers to question 5 in the survey. 

```{r}
survey_app %>%
  mutate(id = id %>% as.character()) %>% 
  left_join(survey %>% 
              select(id ,Q5)) %>% 
  mutate(final_grade =  mc + open) %>% 
  mutate(app_act = scale(max_n) + scale(attempts) + scale(max_consecutive)) %>% 
  select(Class, final_grade, app_act , ends_with("Mean"), Q5) %>% 
  tbl_summary(by = Class) %>% add_n() %>% add_p()
```


## is it possible to look at multiple regression?

```{r}
survey_app %>% 
  mutate(final_grade =  mc + open) %>% 
  ggplot(aes(x = final_grade))+
  geom_histogram(binwidth = 1)
```


```{r}
# -starts_with("mode")
survey_app %>% 
  # mutate(final_grade =  mc + open) %>% 
  select(-mc, -open, -starts_with("mode")) -> lm_data

# lm_data = lm_data[c(-42, -36, -6),]
# lm_data = lm_data[c(-141, -46, -20, -47),]

m2 = lm(sum ~ .-id-GSLCSL_Mean, data = lm_data)
summary(m2)
plot(m2)
```

```{r}

m3 = lm(`Exam grade` ~ 
          `Correct answers`:Attempts+
          `Correct answers`+
          Attempts+
          `Frequency of mode`+
          # max_far+
          # AMG_Mean +
          # APG_Mean+
          TM_Mean+
          Selfeval_Mean+
          Selfefficacy_Mean+ Class,
        data = lm_data %>% 
          .[c(-35, -36, -42, -42, -7, -21, -46, -141, -17, -5, -133),] %>%
          # .[c(-21, -46, -141, -17), ] %>%
          # .[c(-21),] %>% 
                  rename(
    # 'Days in a row' = max_consecutive,
    # "Unique days" = max_n,
    "Early start" = min_far,
    "Late finish" = max_far,
    "Correct answers" = freq_correct,
    "Mean time" = m_time,
    "Minimum time" = min_time,
    "Maximum time" = max_time,
    "Frequency of mode" = freq,
    "Attempts"=attempts,
    "Exam grade" = sum
  )
        )
summary(m3)
plot(m3)
```

```{r}
stargazer::stargazer(m3, type = "text")
```

```{r}
library(sjPlot)
library(sjmisc)
library(ggplot2)
theme_set(theme_sjplot())

plot_model(m3_lp, type = "pred", terms = c("Correct answers", "Attempts"))+
    theme_minimal()+
  theme(legend.position = c(0.8, 0.2))




plot_model(m3, type = "pred", terms = c("Correct answers", "Attempts"))+
    theme_minimal()+
  theme(legend.position = c(0.8, 0.2))+
  theme(text=element_text(size=12,  family="Helvetica"))+
  ylim(-20, 100)

ggsave("sj_1.png", width = 8, height = 5)
# plot_model(m3, type = "pred", terms = c("Selfefficacy_Mean"))
```


```{r}
lm_data %>% 
  ggplot(aes(x = freq, y = sum))+
  geom_point()
```



```{r}
stargazer::stargazer(m2, type = "text")
?stargazer
```


### 4th class

```{r}
df_comb_lp %>%
  full_join(survey_lpa %>% mutate(username = username %>% as.numeric()),
            by = c("id" = "username")) %>% 
  filter(GSL_Mean != "NaN") %>%
  mutate(Class = Class %>% as.character() %>%  replace_na("4") %>% as.factor(),
         across(everything(), ~ replace_na(.x, 0))) %>% 
  select(-open, -mc) %>% 
  mutate(id = id %>% as.character()) %>% 
  left_join(GameAppExam %>% mutate(id = id %>% as.character()))-> survey_app_4

df_comb_lp %>%
  full_join(survey_lpa %>% mutate(username = username %>% as.numeric()),
            by = c("id" = "username")) %>% 
  filter(GSL_Mean != "NaN") %>%
  mutate(Class = Class %>%
           as.character() %>%
            tidyr::replace_na("4") %>%
           as.factor()
         ) %>%
  mutate_all(~ifelse(is.na(.x), mean(.x, na.rm = TRUE), .x))  %>% 
  select(-open, -mc) %>% 
  # mutate(id = id %>% as.character()) %>% 
  left_join(GameAppExam,  by = c("id"="username")) -> survey_app_4_mean

survey_app_4 %>%
  mutate(id = id %>% as.character()) %>% 
  left_join(survey %>% 
              select(id ,Q5)) %>% 
  mutate(final_grade =  mc + open) %>% 
  mutate(app_act = scale(max_n) + scale(attempts) + scale(max_consecutive)) %>% 
  select(Class, final_grade, app_act , ends_with("Mean"), Q5) %>% 
  tbl_summary(by = Class) %>% add_n() %>% add_p()
```


```{r}


kruskal.test(APG_Mean ~ Class ,data = survey_app_4)
```

```{r}
survey_app_4 %>% 
ggplot(aes(x = Class, y = APG_Mean))+
  geom_violin(aes(fill = Class), trim = FALSE) + 
  geom_boxplot(width = 0.2)+
    scale_fill_brewer(palette = "RdBu")+
  theme(legend.position = "none")+
  theme_bw()+
  ggtitle("Open question scores")
```
### only LP model

```{r}
m3_lp_with_class = lm(`Exam grade` ~ 
            `Correct answers`:Attempts + 
            `Correct answers`+
             Attempts+
          `Frequency of mode` + 
            `Unique days`+
            Class +
            `Early start`
          ,
        data = df_comb_lp %>% 
        select(-starts_with("mode"), -mc, -open, -id) %>% 
          mutate(Class = relevel(Class, ref = "1")) %>% 
  .[c(-10, -48, -62, -54, -28),] %>%
    # .[c(-46),] %>%
                      rename(
    "Days in a row" = max_consecutive,
    "Unique days" = max_n,
    "Early start" = min_far,
    "Late finish" = max_far,
    "Correct answers" = freq_correct,
    "Mean time" = m_time,
    "Minimum time" = min_time,
    "Maximum time" = max_time,
    "Frequency of mode" = freq,
    "Attempts"=attempts,
    "Exam grade" = sum)
  )
summary(m3_lp)
plot(m3_lp)
```

```{r}
stargazer::stargazer(m3_lp ,m3_lp_with_class, type = "text")
```

```{r}
stargazer::stargazer(m3, m3_lp, type = "text")
```

```{r}

survey_app_4 %>% 
  # single_imputation() %>% 
  mutate(sum = open+mc) %>% 
  # select(-open, -mc) %>%
  # as_tibble() %>%
  mutate(Class = as.factor(Class)) %>%
  mutate(Class = relevel(Class, ref = 4)) -> lm_data_4

lm_data_4$Class

lm_data_4 %>% 
          # .[c(-16, -140, -97, -6, -41),] %>%
          # .[c(0),] %>% 
            rename("Exam grade" = sum) %>% 
          select(CMG_Mean, CPG_Mean, Selfefficacy_Mean, TM_Mean, Selfeval_Mean, Class, `Exam grade`)

m4 = lm(`Exam grade` ~ 
          # AMG_Mean+
          # APG_Mean+
          CMG_Mean+
          # CPG_Mean+
          Selfefficacy_Mean +
          GSL_Mean+
          # CSL_Mean+
          # GSLCSL_Mean +
          TM_Mean +
          Selfeval_Mean + 
          Class
        ,
        data = lm_data_4 %>% 
          .[c(-17, -141, -181, -7, -42, -13, -207, -104, -155, -73, -193),] %>%
          # .[c(-13, -207, -104, -155, -73, -193),] %>%
            rename("Exam grade" = sum)
)
summary(m4)
plot(m4)
```

### final regression std 

```{r}
m4 = lm(`Exam grade` ~ 
          # AMG_Mean+
          # APG_Mean+
          CMG_Mean+
          # CPG_Mean+
          Selfefficacy_Mean +
          GSL_Mean+
          # CSL_Mean+
          # GSLCSL_Mean +
          TM_Mean +
          Selfeval_Mean + 
          Class
        ,
        data = lm_data_4 %>% 
          .[c(-17, -141, -181, -7, -42, -13, -207, -104, -155, -73, -193),] %>%
          # .[c(-13, -207, -104, -155, -73, -193),] %>%
            rename("Exam grade" = sum)
)
summary(m4)
plot(m4)

lm.beta::lm.beta(m4) 
```



```{r}
survey_app_4_mean$`MC-SCORE (max 60)`

survey_app_4_mean %>% 
  mutate(open = case_when(
    open == "NA" ~ NA_real_,
    TRUE ~ open),
    mc = case_when(
    mc == "NA" ~ NA_real_,
    TRUE ~ mc)
    ) %>% 
  single_imputation() %>% 
  mutate(sum = open+mc) %>% 
  # select(-open, -mc) %>% 
  as_tibble() %>%
  mutate(Class = as_factor(Class)) %>% 
  mutate(Class = stats::relevel(Class, ref = "4"))-> lm_data_4

m4 = lm(sum ~ 
          AMG_Mean+ 
          APG_Mean+
          # CMG_Mean+CPG_Mean+
          Selfefficacy_Mean+
          # GSL_Mean+CSL_Mean+
          TM_Mean+Selfeval_Mean+
          Class,
        data = lm_data_4 %>% .[c(-7, -193, -6, -141, -181, -155),]
)
summary(m4)
plot(m4)
```


```{r}
?stargazer
# stargazer::stargazer(m3, m3_lp, m4, type = "html")
stargazer::stargazer(m3_lp, m3, m4, 
                     type = "html",  
                     single.row=TRUE,
order = c("Constant",
          "`Correct answers`", "Attempts", "`Frequency of mode`", "`Unique days`", "`Early start`", 
"TM_Mean", "Selfeval_Mean", "Selfefficacy_Mean", "CMG_Mean" , "GSL_Mean",  
"Class1","Class2", "Class3"),
                     out = "regression_tables.doc",
                     title = "Final grades model")

tab_model(m3_lp, m3, m4, collapse.ci = TRUE, show.reflvl = TRUE, show.aic = T, title = "Final grades models", p.style = "stars")
?tab_model
```

```{r}
library(gamair)
# data("mpg", package="gamair")

library(mgcv)
# Fit the model
mod_1 <- gam(sum ~ s(AMG_Mean)+ 
          s(APG_Mean)+
          s(CMG_Mean)+s(CPG_Mean)+
          s(Selfefficacy_Mean)+
          s(GSL_Mean)+s(CSL_Mean)+
          s(TM_Mean)+s(Selfeval_Mean)+
          Class
          , data = lm_data_4, method = "REML")

# View the summary
summary(mod_1)
plot(mod_1)
```

```{r}
plot(mod_1, rug = TRUE, residuals = TRUE,
     pch = 1, cex = 1)

plot(mod_1, shade = TRUE, shade.col = "lightblue")

plot(mod_1,  shade = TRUE, shade.col = "lightblue", 
     shift = coef(mod_1)[1], seWithMean = TRUE)
```

```{r}
gam.check(mod_1)
```

```{r}
concurvity(mod_1, full = TRUE)
```

```{r}
stargazer::stargazer(mod_1, type = "text")
```

```{r}
mod_3_lp = gam(sum ~ 
                 s(max_consecutive) +
                 s(max_n) + s(min_far) + s(max_far) +
                 s(freq_correct) + s(attempts) +
                 s(freq),             # s(freq_correct ,attempts),
        data = df_comb_lp %>% select(-starts_with("mode"), -mc, -open, -id, -ends_with("time")) %>% 
          mutate(Class = relevel(Class, ref = "2")), method = "REML")

summary(m3_lp)
plot(m3_lp)

# View the summary
summary(m3_lp)
plot(m3_lp)
```
```{r}
mod_3_lp = gam(sum ~ 
                 max_consecutive +
                 s(max_n) + s(min_far) + s(max_far) +
                 s(freq_correct) + s(attempts) +
                 s(freq) + Class +
                 s(m_time) + s(min_time) + s(max_time) +
                 te(freq_correct, attempts),
        data = df_comb_lp %>% 
          select(-starts_with("mode"), -mc, -open, -id) %>% 
          mutate(Class = relevel(Class, ref = "1")), method = "REML")
summary(mod_3_lp)
plot(mod_3_lp)

?gam
```

### GLM

```{r}
glm4 = glm(`Exam grade` ~ 
          # AMG_Mean+
          # APG_Mean+
          CMG_Mean+
          CPG_Mean+
          Selfefficacy_Mean +
          # GSL_Mean+
          # CSL_Mean+
          GSLCSL_Mean +
          TM_Mean +
          Selfeval_Mean + 
          Class
        ,
        family = "gaussian",
        data = lm_data_4 %>% 
          .[c(-17, -141, -181, -7, -42, -13, -207, -104, -155, -73, -193),] %>%
          # .[c(-13, -207, -104, -155, -73, -193),] %>%
            rename("Exam grade" = sum)
)


summary(glm4)
plot(glm4)

with(summary(glm4), 1 - deviance/null.deviance)
```

# FA

```{r}
library(polycor)
corrr<- hetcor(lm_data_4 %>% select(-id, -Class) %>% select(ends_with("Mean")))
corrr <- corrr$correlations


cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(corrr)

corrplot(corrr,          method="color", col=col(200),  
         type="lower", order="hclust", 
         # addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=30, tl.offset = 0, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.1, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=T )

corrplot(M, 
         # title = "Spearman correlation. Survey and application",
         method="color", col=col(200),  
         type="lower", order="hclust", 
         # addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=30, tl.offset = 0, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=T 
         )
```

```{r}
library(psych)

alpha(corrr)

fa(corrr, nfactors=3, rotate="varimax", fm="ml") 
factor.plot(fa(corrr, nfactors=3, rotate="varimax", fm="ml"))
fa.diagram(fa(corrr, nfactors=3, rotate="oblimin", fm="ml"))

efa_1 <- fa(corrr, nfactors=3, rotate="oblimin", fm="ml", scores = TRUE ,n.obs = 224 , n.iter = 100)
# ?fa
summary(efa_1)
efa_1
fascores <- factor.scores(lm_data_4 %>% select(-id, -Class) %>% select(ends_with("Mean")) %>% as.matrix(), efa_1)


# fascores$scores
```

```{r}
fascores$scores %>% 
  as_tibble() %>% 
  mutate(username = lm_data_4$id %>% as.character(),
          LP = lm_data_4$Class,
         grade_sum = lm_data_4$sum) %>% 
  left_join(survey1 %>% select(username ,age, gender, full_part)) %>% 
  na.omit() %>% 
  select(-username) %>% 
  mutate(full_part = full_part %>%  as.factor(),
         gender = gender %>% as.factor())-> lm_data_FA

lm_data_FA
```

```{r}
lm_fa_1 <- lm(grade_sum~ .-age-gender, data = lm_data_FA)
summary(lm_fa_1)
plot(lm_fa_1)
```

```{r}
gam_fa = gam(grade_sum ~ 
                 LP + 
                 s(ML1)+ s(ML2) + s(ML3) + 
               full_part,
        data = lm_data_FA, method = "REML")
summary(gam_fa)
plot(gam_fa)
```



```{r}
# mfin.model <- 'M1 =~ BSBM14A + BSBM14B + BSBM14C + BSBM14D + BSBM14E
#             M2 =~ BSBM16A + BSBM16B + BSBM16C + BSBM16D + BSBM16E + BSBM16F + BSBM16G + BSBM16H + BSBM16I
#             M3 =~ '
# ?lavaan::cfa
# fit <- lavaan::cfa(fin.model, data = fin)
# semPaths(fit, title = FALSE, curvePivot = TRUE)
# summary(fit, fit.measures = TRUE)
# standardizedSolution(fit)
```

## FA 2

```{r}
survey1 %>% 
  count(username)

survey1 %>% 
  filter(consent == 1) %>% 
  filter(username != 454135) %>% 
  mutate(username = as.numeric(username)) %>% 
  select(-recordeddate, -consent, -age ,-gender, -full_part) %>% 
  na.omit() %>% 
  left_join(GameAppExam %>% mutate_all(as.numeric) %>% unique()) %>% 
  single_imputation() -> survey1_to_fa

survey1 %>% 
  filter(consent == 1) %>% 
  filter(username != 454135) %>% 
  select(-recordeddate, -consent, -age ,-gender, -full_part) %>% 
  single_imputation() %>%
  na.omit() %>% 
  left_join(GameAppExam %>% mutate_all(as.numeric) %>% unique()) %>% 
  single_imputation() -> survey1_to_fa_imputed

# survey1 %>% 
#   filter(consent == 1) %>% 
#   mutate(username = as.numeric(username)) %>%
#   filter(username != 454135) %>% 
#   select(-recordeddate, -consent, -age ,-gender, -full_part) %>% 
#   left_join(GameAppExam %>% mutate_all(as.numeric) %>% unique()) -> survey1_to_fa_missing

GameAppExam %>% mutate_all(as.numeric) 

survey1_to_fa

corrr_s1<- hetcor(survey1_to_fa %>% select(-username))
corrr_s1 <- corrr_s1$correlations


cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(corrr_s1)

corrplot(corrr_s1,          method="color", col=col(200),  
         type="lower", order="hclust", 
         # addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=30, tl.offset = 0, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.1, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=T )

alpha(corrr_s1)

fa(corrr_s1, nfactors=5, rotate="varimax", fm="ml") 
factor.plot(fa(corrr_s1, nfactors=5, rotate="varimax", fm="ml"))
fa.diagram(fa(corrr_s1, nfactors=8, rotate="oblimin", fm="ml"))

efa_2 <- fa(corrr_s1, nfactors=8, rotate="oblimin", fm="ml", scores = TRUE ,n.obs = 224 , n.iter = 20)
# ?fa
summary(efa_2)
efa_2

fascores_2 <- factor.scores(survey1_to_fa %>% select(-username) %>% as.matrix(), efa_2)
```





```{r}
fascores_2$scores %>% 
  as_tibble() %>% 
  mutate(username = survey1_to_fa$username) %>% 
  left_join(survey1 %>% select(username ,age, gender, full_part)) %>% 
  group_by(username) %>% 
  mutate(n = n()) %>% 
  filter(n == 1) %>% 
  select(-n) %>% 
  mutate(full_part = full_part %>%  as.factor(),
         gender = gender %>% as.factor(),
         id = username %>% as.numeric()) %>% 
  left_join(lm_data_4 %>% select(id, Class, sum)) %>% 
  select(-id)-> lm_data_FA_2

lm_data_FA_2
```

```{r}
lm_fa_2 <- lm(sum~ .-username - age - ML5- ML1, data = lm_data_FA_2)
summary(lm_fa_2)
plot(lm_fa_2)
```

## CFA

```{r}
sjmisc::reliab_test(survey1_to_fa %>% select(starts_with("AMG")), scale.items = FALSE, digits = 3)


# - Selfeval_1 - TM_2
C_A = tibble(factor = c( "Selfeval", "GSL", "CSL", "GSLCSL",
                        "Selfefficacy", "TM", "APG" ,
                        "CMG" ,"CPG" ,"AMG"), 
             std.alpha = c(0.7040792 ,0.6081533, 0.5428689, 0.72145,
                           0.8962932 ,0.7555768 ,0.8413274, 
                           0.8577257 ,0.9018892, 0.8163391))

# library(gtsummary)
C_A %>% 
  arrange(std.alpha)
# psych::alpha(survey1_to_sem_missings %>% 
#                    select(starts_with("CSL"), starts_with("GSL")))
```


Selfeval_Mean
Selfefficacy_Mean
GSL_Mean


```{r}
names(survey1_to_fa) %>% as_tibble() %>% arrange(value)
```

```{r}
# survey1_to_sem_missings %>%
#   select(starts_with("Selfeval"),  starts_with("GSL")) %>% na.omit() %>%
#   cor()
# 
# corrplot()


M<-survey1_to_sem_missings %>%
  select(starts_with("Selfeval"),  
         starts_with("GSL"), -GSL_3, -GSL_5, 
         starts_with("Selfefficacy"), 
         starts_with("TM"),
         starts_with("APG"),
         starts_with("CMG"),
         starts_with("CPG"),
         starts_with("CSL") ,
         starts_with("GSL"), 
         starts_with("AMG"),
         final_grade) %>% na.omit() %>%
  cor()


# matrix of the p-value of the correlation
# p.mat <- cor.mtest(M)
# head(p.mat[, 1:5])

p.mat <- cor.mtest(M, conf.level = .95, method = "spearman")
# ?cor.mtest
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
# pdf(file = "corplot.pdf")
png(filename = "corrpot_final.png" ,width = 1000, height = 1000)
corrplot(M, 
         # title = "Spearman correlation. Survey and application",
         method="color", col=col(200),  
         type="lower", 
         # order="hclust", 
         # addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=30, tl.offset = 0, tl.cex = 1.2/par("cex"), #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=T 
         )
dev.off()
```

```{r}

```


```{r}



mfin.model <- 'AMG =~ AMG_1 + AMG_2 + AMG_3 + AMG_4
   APG =~ APG_1 + APG_2 + APG_3 + APG_4
   CMG =~ CMG_1+ CMG_2 + CMG_3 + CMG_4 + CMG_5 + CMG_6 + CMG_7 + CMG_8
   CPG =~ CPG_1 + CPG_2 + CPG_3 + CPG_4 + CPG_5 + CPG_6 + CPG_7 + CPG_8
   # CSL =~ CSL_1 + CSL_2 + CSL_3
   GSL =~ GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5
   # CSLGSL =~ CSL_1 + CSL_2 + CSL_3 + GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5
   Selfefficacy =~ Selfefficacy_0 + Selfefficacy_2 + Selfefficacy_3 + Selfefficacy_4 + Selfefficacy_5 + Selfefficacy_6 + Selfefficacy_7 + Selfefficacy_8
   # Selfeval =~ selfeval_2 + selfeval_3 + Selfeval_4 + Selfeval_5 + Selfeval_6
   TM =~ TM_1 + TM_3 + TM_4 + TM_5 + TM_6 + TM_7_reversed + TM_8_reversed
'

# mfin.model <- 'Selfefficacy =~ Selfefficacy_0 + Selfefficacy_2 + Selfefficacy_3 + Selfefficacy_4 + Selfefficacy_5 + Selfefficacy_6 + Selfefficacy_7 + Selfefficacy_8
#    Selfeval =~ Selfeval_1 + selfeval_2 + selfeval_3 + Selfeval_4 + Selfeval_5 + Selfeval_6
#    # GSL =~ GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5
#    TM =~ TM_1 + TM_3 + TM_4 + TM_5 + TM_6 + TM_7_reversed + TM_8_reversed
# '

fit <- lavaan::cfa(mfin.model, data = survey1_to_sem_missings , 
                   estimator = "MLR", missing = "fiml")

# library(semPlot)
semPaths(fit, "par", weighted = FALSE, nCharNodes = 7, shapeMan = "rectangle",
         sizeMan = 8, sizeMan2 = 10)

lavInspect(fit, "cor.lv")

# summary(fit)

# ?semPaths
lavaan::summary(fit, fit.measures = TRUE)

standardizedSolution(fit)

poor_model_scores <- lavPredict(fit) %>% 
  as_tibble() %>% 
  mutate_all(as.numeric) %>% 
  mutate(username = survey1_to_sem_missings$username, 
         class = survey1_to_sem_missings$Class, 
         final_grade = survey1_to_sem_missings$final_grade)

poor_model_scores %>% 
  left_join(survey1_to_sem %>% 
              select(starts_with("CPG"), username) %>% 
              mutate(username = username %>% as.numeric())) %>% 
  na.omit() %>% 
  group_by(username) %>% 
  mutate(CPG_mean = sum(CPG_1 ,CPG_2 ,CPG_3 ,CPG_4 ,CPG_5 ,CPG_6 ,CPG_7))
  select(-username) %>% 
  tbl_summary(by = class) %>% 
  add_n() %>% 
  add_p() %>% 
  modify_header(label = "**Factor**") %>% # update the column header
  bold_labels() %>% 
  # add_stat_label(location = NULL, label = NULL)
#%>% 
  #   as_gt() %>%
  # gt::gtsave(filename = "anova_factor.html")
    as_flex_table() %>%
  flextable::save_as_docx(path = "ANOVA_FOR_FACTORS.docx")


poor_model_scores %>% 
  select(-username) %>%
  tbl_summary(
    by = class,
    statistic = list(all_continuous() ~ "{median} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = all_continuous() ~ 2,
    # label = grade ~ "Tumor Grade",
    missing_text = "(Missing)"
  )
```



    modify_header(label = "**Variable**") %>% # update the column header
  bold_labels() Comparative Fit Index (CFI)                    0.976+
  Tucker-Lewis Index (TLI)                       0.928+
  RMSEA                                          0.128-
  SRMR                                           0.031+

e used three measures of goodness of fit recommended 
by the majority of modern SEM guidebooks: CFI (Comparative Fit Index), acceptable CFI values ≥ 0.90; 
RMSEA (Root Mean Square Error of Approximation), 
acceptable RMSEA values ≤ 0.05; and SRMR
(Standardized Root Mean Square Residual), acceptable SRMR values ≤ 0.08. 

These are indicators of differences between the original 
covariance matrix and the matrix of covariances of the model, which 
allow the researcher to measure the goodness of fit of a model to a set 
of observations [Nasledov 2012: 348–353]. A comparison of f


```{r}
survey1_to_fa %>% 
  left_join(survey1 %>% select(username ,age, gender, full_part)) %>% 
  group_by(username) %>% 
  mutate(n = n()) %>% 
  filter(n == 1) %>%
  ungroup() %>% 
  select(-n) %>% 
  mutate(full_part = full_part %>%  as.factor(),
         gender = gender %>% as.factor(),
         id = username %>% as.numeric()) %>% 
  left_join(lm_data_4 %>% select(id, Class, sum)) %>% 
  select(-id)-> survey1_to_sem

# survey1_to_sem$survey1_to_sem

survey1_to_sem %>% 
  sjmisc::to_dummy(Class, suffix = "label") %>% 
  bind_cols(survey1_to_sem) -> survey1_to_sem


set.seed(42)
survey1_to_fa_imputed %>%
  left_join(df_comb_lp %>% 
              select(id, Class) %>% 
              rename(username = id) %>% 
              mutate(Class = Class %>% as.numeric())) %>% 
  mutate(Class = Class %>% tidyr::replace_na(4) %>% as.factor()) %>% 
  mutate(Class = stats::relevel(Class, ref = "4")) %>% 
  sjmisc::to_dummy(Class, suffix = "label") %>% 
  bind_cols(survey1_to_fa_imputed) %>% 
  rename(test_grades = MC.SCORE..max.60.,
         open_grades = Open.ended.questions..max.40.) %>% 
  mutate(final_grade = test_grades + open_grades) %>% 
    filter(final_grade < 100)-> survey1_to_sem_imputed


survey1 %>%
  filter(consent == 1) %>%
  mutate(username = as.numeric(username)) %>%
  filter(username != 454135) %>%
  select(-recordeddate, -consent,) %>%
  left_join(GameAppExam %>% mutate_all(as.numeric) %>% unique()) %>%
  left_join(df_comb_lp %>%
              select(id, Class) %>%
              rename(username = id) %>%
              mutate(Class = Class %>% as.numeric())) %>%
  mutate(Class = Class %>% tidyr::replace_na(4) %>% as.factor()) %>%
  mutate(Class = stats::relevel(Class, ref = "4")) -> survey1_to_fa_missings

survey1_to_fa_missings %>%
  sjmisc::to_dummy(Class, suffix = "label") %>%
  bind_cols(survey1_to_fa_missings) %>%
  rename(test_grades = `MC-SCORE (max 60)`,
         open_grades = `Open-ended questions (max 40)`) %>%
  mutate(final_grade = test_grades + open_grades) %>%
  mutate(TM_3 =TM_3 %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8),
         TM_7_reversed = TM_7_reversed %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8),
         TM_8_reversed = TM_8_reversed %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8))  -> survey1_to_sem_missings

survey1_to_sem_missings$final_grade
```

### MICE

```{r}

```



```{r}
??mvn
# library(MVN)
MVN::mvn(data = survey1_to_sem_imputed %>% select(-username, -starts_with("Class")))
```


```{r}

mfin.model_sem <- '
# Measurement model
Selfefficacy =~ Selfefficacy_0 + Selfefficacy_2 + Selfefficacy_3 + Selfefficacy_4 + Selfefficacy_5 + Selfefficacy_6 + Selfefficacy_7 + Selfefficacy_8
   Selfeval =~  selfeval_2 + selfeval_3 + Selfeval_4  + Selfeval_5 + Selfeval_6 
   TM =~ TM_1 +  TM_3 + TM_4 + TM_5 + TM_6 + TM_7_reversed + TM_8_reversed
   
   # Final_grade <~ test_grades + open_grades
   
# Structural model 
# Regressions

final_grade ~ Selfefficacy * TM + Class_1 + Class_2 + Class_3 + TM + Selfefficacy + Selfeval

final_grade ~ 1
'

fit_sem <- lavaan::sem(mfin.model_sem, data = survey1_to_sem_missings %>% 
                         # na.omit() %>%
                    filter(!username %in% c(73834, 453095 ,485167, 479665))
                         # mutate(final_grade = final_grade %>% scale())
                       ,missing = "fiml" , meanstructure=F, 
                       ridge = T,
                       estimator = "MLR")
fit_sem
# ULS 
# DWLS
# ULSMV
# ULSMVS
# WLSMV 
?sem

?semPaths
semPaths(fit_sem, what = "col", whatLabels = "par", style = "mx", 
         rotation = 2, layout = "tree2", mar = c(1, 2, 1, 2), nCharNodes = 7,
         shapeMan = "rectangle", sizeMan = 8, sizeMan2 = 5, 
         filetype = "jpg", filename = "SEM")
```

```{r}
# ?fitMeasures
fitMeasures(fit_sem, 
            fit.measures = c("chisq", "df", "pvalue", "cfi", "rmsea", "tli", "SRMR"), 
            output = "text")
```


```{r}
lavaan::summary(fit_sem, fit.measures = TRUE, standardized = TRUE, rsq=TRUE)
```

```{r}
# lm_data_4 %>% 
#   sjmisc::to_dummy(Class, suffix = "label") %>% 
#   bind_cols(lm_data_4) -> lm_data_4_to_sem
# 
# model_mean = '
#   # Structural model 
#   # Regressions
#   sum ~ Selfefficacy_Mean + GSL_Mean + Selfeval_Mean + Class_1 + Class_2 + Class_3
# 
#   sum ~ 1'
# 
# fit_sem_reg <- lavaan::sem(model_mean, data = lm_data_4_to_sem)
# fit_sem_reg
# 
# lavaan::summary(fit_sem_reg, fit.measures = TRUE ,rsq=TRUE)
```

```{r}
?semPaths
semPaths(fit_sem, what = "col", whatLabels = "par", style = "mx", 
         rotation = 2, layout = "tree2", mar = c(1, 2, 1, 2), nCharNodes = 7,
         shapeMan = "rectangle", sizeMan = 8, sizeMan2 = 5)
```

```{r}
survey1_to_fa %>% 
  left_join(survey1 %>% 
              select(username ,age, gender, full_part) %>% 
              mutate(username = username %>% as.numeric())) %>% 
  group_by(username) %>% 
  mutate(n = n()) %>% 
  filter(n == 1) %>%
  ungroup() %>% 
  select(-n) %>% 
  mutate(full_part = full_part %>%  as.factor(),
         gender = gender %>% as.factor(),
         id = username %>% as.numeric()) %>% 
  left_join(lm_data_4 %>% select(id, Class, sum)) %>% 
  select(-id)-> survey1_to_sem

# survey1_to_sem$survey1_to_sem

reverse_scale <- function(x){
    return(max(x)-x + 1)
}

survey1_to_sem %>% 
  sjmisc::to_dummy(Class, suffix = "label") %>% 
  bind_cols(survey1_to_sem) %>% 
  mutate(TM_3 = reverse_scale(TM_3), 
         TM_7_reversed = reverse_scale(TM_7_reversed), 
         TM_8_reversed = reverse_scale(TM_8_reversed))-> survey1_to_sem_fixed


# survey1_to_fa_missing$TM_1 %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8)
# 
# survey1_to_fa_missing %>% 
#   left_join(lm_data_4 %>% select(id, Class, sum), by = c("username" = "id")) %>% 
#   sjmisc::to_dummy(Class, suffix = "label") %>% 
#   bind_cols(survey1_to_fa_missing) %>% 
#     mutate(TM_3 =TM_3 %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8), 
#          TM_7_reversed = TM_7_reversed %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8), 
#          TM_8_reversed = TM_8_reversed %>% replace_na(value = 0) %>% reverse_scale() %>% na_if(8)) -> survey1_to_sem_missings
```



```{r}
survey1_to_sem_fixed %>%
  select(starts_with("CMG")) %>%
  # select(-TM_3,  -TM_7_reversed , - TM_8_reversed)%>%
  psych::alpha()
# 
# survey1_to_sem %>% 
#   select(starts_with("TM")) %>% 
#   psych::alpha(keys = c("TM_3",  "TM_7_reversed" , "TM_8_reversed"))
  

# survey1_to_sem %>% 
#   select(starts_with("TM")) %>% 
#   cor()
# ?alpha

# AMG =~ AMG_1 + AMG_2 + AMG_3 + AMG_4
   # APG =~ APG_1 + APG_2 + APG_3 + APG_4
   # CMG =~ CMG_1+ CMG_2 + CMG_3 + CMG_4 + CMG_5 + CMG_6 + CMG_7 + CMG_8
   # CPG =~ CPG_1 + CPG_2 + CPG_3 + CPG_4 + CPG_5 + CPG_6 + CPG_7 + CPG_8
   # CSL =~ CSL_1 + CSL_2 + CSL_3
   # GSL =~ GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5

mfin.model_sem_3 <- '
# Measurement model
Selfefficacy =~ Selfefficacy_0 + Selfefficacy_2 + Selfefficacy_3 + Selfefficacy_4 + Selfefficacy_5 + Selfefficacy_6 + Selfefficacy_7 + Selfefficacy_8
   Selfeval =~ Selfeval_1 + selfeval_2 + selfeval_3 + Selfeval_4 + Selfeval_5 + Selfeval_6
   GSL =~ GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5
   
   # SelfevalGSL =~ Selfeval + GSL
   
# Structural model
# Regressions

sum ~ Selfefficacy + Selfeval + GSL + Class_1 + Class_2 + Class_3

sum ~ 1
'
set.seed(2)
fit_sem_3 <- lavaan::sem(mfin.model_sem_3, data = survey1_to_sem_fixed %>% select(-username) %>% na.omit() %>% mutate(sum = scale(sum)), meanstructure=F ,ridge = T, estimator = "MLM")
# DWLS
# ULSMV
# WLSMV 
# estimator = "MLM")
varTable(fit_sem_3)
fit_sem_3

semPaths(fit_sem_3, what = "col", whatLabels = "par", style = "mx", 
         rotation = 2, layout = "tree2", mar = c(1, 2, 1, 2), nCharNodes = 7,
         shapeMan = "rectangle", sizeMan = 8, sizeMan2 = 5)
```

```{r}
lavaan::summary(fit_sem_3, fit.measures = TRUE ,rsq=TRUE, standardized = F)
```


```{r}
?lavInspect
lavaan::lavInspect(fit_sem_3, "cor.lv")
```

```{r}
# library(polycor)
corrr_3<- polycor::hetcor(survey1_to_sem_fixed %>% 
                 select(-username, -Class) %>% 
                 select(
                   starts_with("Selfefficacy"),
                   starts_with("Selfeval"),
                   starts_with("TM"),
                   starts_with("GSL")
                   )
               )
corrr_3 <- corrr_3$correlations

corrr_3

efa_3 <-  psych::fa(corrr_3, nfactors=4, rotate="oblimin", fm="ml", scores = TRUE ,n.obs = 224)
efa_3

# png(filename = "FA.png", width = 1200)
pdf(file = "FA.pdf")
psych::fa.diagram(efa_3)
dev.off()

?fa
```

```{r}
# stargazer::stargazer(fit_sem_3, summary=FALSE, type='text', rownames=FALSE, initial.zero=FALSE, digits=3, title='Predicting Y')
```

## SEM PLOTS

```{r}
library(tidySEM)
graph_sem(model = fit_sem_3)
```

```{r}
# ?semPaths
semPaths(fit_sem,
         title = T,
         curvePivot = TRUE,
         what = "std",
         rotation = 3,
         layout = "tree2",
         optimizeLatRes = TRUE,
         intercepts = FALSE,
         edge.label.cex = 0.95,
         exoVar=T,
         sizeMan=5,
         sizeLat=7,
         nCharNodes=5,
         residuals=T,
         fixedStyle=1,
         freeStyle=1,
         curvePivot = T,
         thresholds = FALSE)
```

```{r}
library(mvoutlier)

plot(survey1_to_sem_fixed)

Y <- survey1_to_sem_fixed %>% 
  # filter(!username %in% c(478845 ,479549 ,485167 ,482613 ,73834)) %>% 
  select(-starts_with("Class"), -sum, -age, -gender ,-full_part) %>% 
  column_to_rownames("username") %>% 
  mutate_all(as.numeric) %>% 
  as.matrix()

res <- aq.plot(Y ,quan =0.95 ,alpha = 0.1)
?aq.plot

478845
479549

485167
482613
73834

res$outliers %>% 
  enframe() %>% 
mutate(name = name %>% as.numeric()) %>% 
  arrange(name) %>% 
  filter(name %in% c(478845 ,479549 ,485167 ,482613 ,73834))
```

```{r}
library(faoutlier)
#Confirmatory with lavaan
model_test <- 'F1 =~  Remndrs + SntComp + WrdMean
F2 =~ MissNum + MxdArit + OddWrds
F3 =~ Boots + Gloves + Hatchts'

(FS_test <- forward.search(holzinger, model_test))
(FS.outlier <- forward.search(holzinger.outlier, model_test))
plot(FS_test)
plot(FS.outlier)
```


```{r}
(FS <- forward.search(survey1_to_sem_fixed %>% na.omit(), mfin.model_sem_3))
# (FS.outlier <- forward.search(holzinger.outlier, mfin.model_sem_3))
plot(FS)
# plot(FS.outlier)
```

```{r}
# fscores_sem_3 <- lavPredict(fit_sem)

fscores_sem_3 <- lavPredict(fit_sem)

fscores_sem_3 %>% 
  as_tibble() %>% cor()

fscores_sem_3 %>% 
  as_tibble() %>% 
  bind_cols(survey1_to_sem_missings %>% 
              filter(!username %in% c(73834, 453095 ,485167, 479665))) -> lm_fscores


lm_fscores %>% 
  filter(Class_4 == 0)

m5 = lm(final_grade ~ 
          Class*Selfefficacy +
          Class*TM +
          Selfeval+
          # Class*Selfeval +
          Class 
        ,data = lm_fscores %>% 
    dplyr::select(Class, Selfefficacy, TM ,Selfeval ,username, final_grade) %>%
          filter(!username %in% c(73834, 453095 ,485167, 479665, 460484, 478886, 459028)) %>%
          column_to_rownames("username"))

summary(m5)
plot(m5)

lm_fscores %>% 
          filter(username %in% c(73834, 453095 ,485167, 479665)) %>% 
  left_join(cooks.distance(m5) %>% 
              enframe(name ="username", value =  "cooks.distance") %>% 
              mutate(username = username %>% as.numeric()))
# car::vif(m5)
```

```{r}
?stargazer

stargazer::stargazer(m5, 
                     type = "html",  out = "final_regression.html",
                     single.row=F)
```


```{r}
library(sjPlot)


plot_model(m5, type = "pred", terms = c("Selfefficacy" ,"TM", "Class"))+
    theme_minimal()+
  # theme(legend.position = c(0.8, 0.2))+
  theme(text=element_text(size=12,  family="Helvetica"))

plot_model(m5, type = "pred", terms = c("Selfefficacy" ,"Class"))+
    theme_minimal()+
  theme(legend.position = c(0.8, 0.2))+
  theme(text=element_text(size=12,  family="Helvetica"))+
  xlab("Self-efficacy")+
  scale_colour_brewer(palette = "Set1")+
    scale_colour_hue(name = "Class",
    # breaks=c("mb", "ma", "mc"),
    labels=c("Non users", "Disengaged", "Active" ,"Utilitarian"))


plot_model(m5, type = "pred", terms = c("TM", "Class"))+
    theme_minimal()+
  theme(legend.position = c(0.8, 0.2))+
  theme(text=element_text(size=12,  family="Helvetica"))+
  xlab("Time-management")+
  scale_colour_brewer(palette = "Set1")+
    scale_colour_hue(name = "Class",
    # breaks=c("mb", "ma", "mc"),
    labels=c("Non users", "Disengaged", "Active" ,"Utilitarian"))




plot_model(m5, type = "pred", terms = c("Selfeval"))+
    theme_minimal()+
  # theme(legend.position = c(0.8, 0.2))+
  theme(text=element_text(size=12,  family="Helvetica"))+
  xlab("Self-evaluation")
```

## robust

```{r}
library(MASS)
rm5 = rlm(final_grade ~ 
          # AMG_Mean+
          # APG_Mean+
          # CMG+
          # CPG_Mean+
          Class*Selfefficacy +
          # GSL+
          # CSL_Mean+
          # GSLCSL_Mean +
          Class*TM +
          Class*Selfeval +
          Class 
        ,data = lm_fscores %>% 
          # filter(final_grade< 85) %>% 
          filter(!username %in% c(73834, 453095 ,485167, 479665)) %>%
          column_to_rownames("username")
         ,psi = psi.bisquare)

summary(rm5)
```



```{r}
iweights <- data.frame(user = lm_fscores %>% 
                         dplyr::select(Class, Selfefficacy, TM ,Selfeval ,username, final_grade) %>% 
                         na.omit() %>% 
                         .$username,
                       resid = rm5$resid,
                       weight = rm5$w)

iweights %>% arrange(weight)
biweights2 <- biweights[order(rr.bisquare$w), ]
biweights2[1:15, ]
```

## bootstrap

```{r}


sample.data = lm_fscores %>% 
    dplyr::select(Class, Selfefficacy, TM ,Selfeval ,username, final_grade)

# Containers for the coefficients
# sample_coef_intercept <- NULL
# sample_coef_x1 <- NULL
sample_coefs <- tibble()

for (i in 1:1000) {
  #Creating a resampled dataset from the sample data
  sample_d = sample.data[sample(1:nrow(sample.data), nrow(sample.data), replace = TRUE), ]
  
  #Running the regression on these data
  model_bootstrap <- lm(final_grade ~ 
          Class*Selfefficacy +
          Class*TM +
          Class*Selfeval +
          Class, data = sample_d)
  
  #Saving the coefficients
  # sample_coef_intercept <-
  #   c(sample_coef_intercept, model_bootstrap$coefficients[1])
  # 
  # sample_coef_x1 <-
  #   c(sample_coef_x1, model_bootstrap$coefficients[2])
  
  sample_coefs <- sample_coefs %>% 
    bind_rows(model_bootstrap$coefficients %>% 
    enframe(name = "coef") %>% 
    mutate(iteration = i)
    )
}
```

```{r}
# means.boot = c(mean(sample_coef_intercept), mean(sample_coef_x1))
# 
# knitr::kable(round(
#   cbind(
#     population = coef(summary(population.model))[, 1],
#     sample = coef(summary(sample.model))[, 1],
#     bootstrap = means.boot),4), 
#   "simple", caption = "Coefficients in different models")

m5$coefficients %>% 
    enframe(name = "coef") %>% 
  mutate(model = "population") %>% 
  bind_rows(
sample_coefs %>% 
  group_by(coef) %>% 
  summarise(value = mean(value)) %>% 
  mutate(model = "bootstrap")
) %>% 
  tidyr::pivot_wider(names_from = model, values_from = value)

confint(population.model)
confint(sample.model)
```

```{r}

summary_m5 = summary(m5)$coefficients %>% 
  as.data.frame() %>% 
  rename(p_value = `Pr(>|t|)`) %>% 
  rownames_to_column("coef")

# summary_m5$`Pr(>|t|)`

summary_m5 %>% 
  dplyr::select(coef, p_value) %>% 
  left_join(
sample_coefs %>% 
  group_by(coef) %>% 
  summarise("boot 2.5 %" = quantile(value, prob = 0.025), 
            "boot 97.5 %" = quantile(value, prob = 0.975)) 
) %>% 
  bind_cols(confint(m5) %>% as_tibble()) %>% 
  # mutate(p_value = p_value %>% round(3)) %>% 
  # kableExtra::kable() %>% 
  gt::gt() %>% 
    tab_header(
    title = "Liner regression coefficients bootstrap"
  ) %>% tab_style(
    style = list(
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = "p_value",
      rows = p_value <= 0.05
    )
  ) %>%  
  tab_footnote(
    footnote = "Adjusted R-squared:  0.358 of population LM",
    locations = cells_column_labels(
      columns = "p_value"
    )
  ) %>% gtsave(filename = "bootstrap.html")

options(digits = 3)
options(scipen = 5)
```


```{r}
library(mgcv)
# detach(mgcv)
# Fit the model
?gam
mod_5 <- mgcv::gam(final_grade ~ 
               s(Selfefficacy)+ 
               s(TM)+
               s(Selfeval)+
               Class
          , data = lm_fscores %>% 
            dplyr::select(Class, Selfefficacy, TM ,Selfeval ,username, final_grade) %>% 
            na.omit(), method = "REML")

# View the summary
summary(mod_5)
plot(mod_5)
```


```{r}
remotes::install_github("ecmerkle/blavaan", INSTALL_opts = "--no-multiarch")
```

```{r}
library("blavaan")
future::plan("multicore")


model_b <- '
# Measurement model
Selfefficacy =~ Selfefficacy_0 + Selfefficacy_2 + Selfefficacy_3 + Selfefficacy_4 + Selfefficacy_5 + Selfefficacy_6 + Selfefficacy_7 + Selfefficacy_8
   Selfeval =~ Selfeval_1 + selfeval_2 + selfeval_3 + Selfeval_4 + Selfeval_5 + Selfeval_6
   GSL =~ GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5
   
   # Final_grade <~ test_grades + open_grades
# Structural model 
# Regressions

# test_grades ~ Selfefficacy + Selfeval + GSL + Class_1 + Class_2 + Class_3
# open_grades ~ Selfefficacy + Selfeval + GSL + Class_1 + Class_2 + Class_3
final_grade ~ Selfefficacy + Selfeval + GSL + Class_1 + Class_2 + Class_3

# test_grades ~~ open_grades

final_grade ~ 1
# test_grades ~ 1
# open_grades ~ 1
'

# fit_sem <- lavaan::sem(model_b, data = survey1_to_sem_imputed 
#                        %>% mutate(final_grade = final_grade %>% scale())
#                        , meanstructure=F, ridge = T, estimator = "ULS")
# ?bsem
fit_bsem <- bsem(model_b, data = survey1_to_sem_imputed, bcontrol=list(cores=4))
summary(fit_bsem)
```

```{r}
summary(fit_bsem, neff=TRUE)
```

```{r}
plot(fit_bsem, pars=5:10, plot.type="trace")
plot(fit_bsem, pars=1:4, plot.type="acf")
```

```{r}
blavPredict(fit_bsem)
```


## mice

```{r}
library("survey")
library("mice")
library("mitools")
library("semTools")
library("lavaan")
library("lavaan.survey")
```

```{r}

model_sem_mice <- '
# Measurement model
Selfefficacy =~ Selfefficacy_0 + Selfefficacy_2 + Selfefficacy_3 + Selfefficacy_4 + Selfefficacy_5 + Selfefficacy_6 + Selfefficacy_7 + Selfefficacy_8
   Selfeval =~ Selfeval_1 + selfeval_2 + selfeval_3 + Selfeval_4 + Selfeval_5 + Selfeval_6
   GSL =~ GSL_1 + GSL_2 + GSL_3 + GSL_4 + GSL_5
   
   # Final_grade <~ test_grades + open_grades
   
# Struc
# test_grades ~ Selfefficacy + Selfeval + GSL
# open_grades ~ Selfefficacy + Selfeval + GSL
# Final_grade ~ Selfefficacy + Selfeval + GSL + Class_1 + Class_2 + Class_3
final_grade ~ Selfefficacy + Selfeval + GSL + Class_1 + Class_2 + Class_3

# test_grades ~~ open_grades

# final_grade ~ 1
# test_grades ~ 1
# open_grades ~ 1
'

?runMI
out1 <- runMI(model_sem_mice, 
              data=survey1_to_sem_missings %>% 
                select(-Class, -Class_4, -username),
              m = 10, 
              miPackage="mice",
              fun="sem",
              meanstructure = TRUE,
              ridge = T, estimator = "MLR")

summary(out1, ci = T, stand = TRUE, rsq = TRUE)
fitMeasures(out1, "chisq")

```


# ridges

```{r}
library(ggridges)

survey1_to_sem_missings %>% 
  # select(-starts_with("Class"), -username, -ends_with("grades"),- final_grade) %>% 
  select(starts_with("Self") , starts_with("GSL")) %>%
  tidyr::pivot_longer(everything(), names_to = "Question", values_to = "Likert") %>% 
ggplot(aes(x = Likert, y = Question, height = stat(density))) + 
  geom_density_ridges(stat = "binline", bins = 7, scale = 0.95, draw_baseline = FALSE)

```

Model 1 : In this model we use application data as predictors and exam grade as an outcome, so that we could understand which components of profiles are the strongest predictors for the final grade. Latent Profiles included as a control variable with Disengaged students as reference level, however even with control for attempts and frequency of correct answers, engagement profile remains significant, i.e. disengaged students on average scored 10 point less at the exam, compared to active and utilitarian. While more time that students spend in the mobile application negatively correlates with final grade, we believe that that effect was introduced by interaction effect. Thus, students with a small number of attempts achieve roughly similar grades, no matter what proportion of these attempts were correct. The best interpretation here will be the least interesting, but if a student answered less than lets say 50 questions, we simply could not be sure that the frequency of correct answers connected with students knowledge and not just a noise, luck or random clicking. Further, students with less than a 75% of correct answers do score less more attempts they made, but after 80% correct attempts additional attempts positively connected with final grade. See figure sjplot_1. That is a strong indicator of ambiguous influence of application on a studying process. In this way, students who know the subject well enough (75-80%) will master the knowledge through repetition in the app, but students who did not know the subject could not get the knowledge necessary for the exam through the application.


Model 2: app users AND answered in the survey, making more attempts slightly reduce final grade, but that is only true for students with small amounts of attempts. Also, there is an interactive effect between the number of attempts and frequency of correct answers, so students who make many mistakes do not benefit from prolonged use of the application, while students who correctly answer questions more frequently highly benefit from using the application for a long time. Self Efficacy strongly positively influences student performance. In addition, the more time students spend in test and practice modes, the higher grade they receive, compared to gamified modes.
game modes negatively influence student performance and that supported by user study, since test and practice were evaluated higher than battle and compete (LINK to usability study)

Model 3 : The final model includes students who agreed to participate in study, if missing values appeared in single or two columns, they were imputed with mice Buuren  & Groothuis-Oudshoorn (2010) following Buuren (2018), observations with more missing were removed.  Application engagement data was reduced to a single variable of a Class, therefore all students who did not use an application naturally formed Class 4 that technically will have zeros in all application metrics. It was used as a reference level in the model. All students who used the app score significantly higher grades than students who choose not use it at all.



### final data info

```{r}
super_final = lm_fscores %>% 
    dplyr::select(Class, Selfefficacy, TM ,Selfeval ,username, final_grade) %>%
          filter(!username %in% c(73834, 453095 ,485167, 479665, 460484, 478886, 459028)) %>% 
  na.omit()

super_final %>% 
  na.omit() %>% 
  left_join(survey1 %>% 
              mutate(username = username %>% as.numeric())) %>% 
  # .$gender %>% table()
  filter(Class ==4)
```

```{r}
scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

poor_model_scores %>% 
  left_join(survey1_to_sem %>% 
              select(starts_with("CPG"), starts_with("GSL"), username) %>% 
              mutate(username = username %>% as.numeric())) %>% 
  filter(username %in% super_final$username) %>% 
  group_by(username) %>% 
  mutate(CPG_scaled = sum(CPG_1 ,CPG_2 ,CPG_3 ,CPG_4 ,CPG_5 ,CPG_6 ,CPG_7, CPG_8),
         GSL_scaled = sum(GSL_1, GSL_2, GSL_3, GSL_4, GSL_5)) %>% 
  ungroup() %>% 
  mutate(CPG_scaled = scale_this(CPG_scaled),
         GSL_scaled = scale_this(GSL_scaled)) %>% 
  select(-username, 
         -CPG_1 ,-CPG_2 ,-CPG_3 ,-CPG_4 ,-CPG_5 ,-CPG_6 ,-CPG_7 ,-CPG_8,
         -GSL_1, -GSL_2, -GSL_3, -GSL_4, -GSL_5) %>%
  tbl_summary(by = class) %>% 
  add_n() %>% 
  add_p() %>% 
  modify_header(label = "**Factor**") %>% # update the column header
  bold_labels() %>% 
  # add_stat_label(location = NULL, label = NULL)
#%>% 
  #   as_gt() %>%
  # gt::gtsave(filename = "anova_factor.html")
    as_flex_table() %>%
  flextable::save_as_docx(path = "ANOVA_FOR_FACTORS_new.docx")
```

